### 2017-01-17 secorder-rdsa-ih.tex
sir corrections 2,3chap only

\chapter{Second-order RDSA with improved hessian estimation (2RDSA-IH)}
\label{sec:2rdsa-ih}
The second-order RDSA with improved Hessian estimate performs an update iteration as follows:
\begin{align}
\label{eq:e2rdsa}
\theta_{n+1} = & \; \theta_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(\theta_n), \\
\overline H_n = & \; (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n),\label{eq:2rdsa-H}
\end{align}
where $\widehat\nabla f(\theta_n)$ is the estimate of $\nabla f(\theta_n)$, 
 %and this corresponds to  the uniform  and   asymmetric Bernoulli variant gradient estimates proposed in \cite{prashanth2015rdsa}.
$\overline H_n$ is an estimate of the true Hessian ${\nabla}^2 f(\cdot)$, $\Upsilon(\cdot)$ projects any matrix onto the set of positive definite matrices and $\{a_n, n\ge 0\}$ is a step-size sequence that satisfies standard stochastic approximation conditions. There are standard procedures such as Cholesky factorization, see \cite{bert22}, for projecting a given square matrix to set of positive definite matrices. Moreover, in the vicinity of a local minimum, one expects the Hessian to be positive definite. In such a case, $\Upsilon$ will represent the identity operator.

@@

On the other hand, $\widehat H_n$ is identical to that in 2RDSA, i.e., it estimates the true Hessian in each iteration using $3$ function evaluations. %Further, $\widehat H_0 = I$. 
For the sake of completeness, we provide below the construction for $\widehat\nabla f(\theta_n)$ and $\widehat H_n$ using asymmetric Bernoulli perturbations, before we present the feedback term that reduces the error in $\widehat H_n$.

@@

 \item \textbf{Execution}: \\
 \For{$n \gets 0,1,2, \ldots, $} {
 \begin{itemize}
 \item Generate $\{d_n^{i}, i=1,\ldots,N\}$, independent of $\{d_m, m=0,1,\ldots,n-1\}$.  
 \item For any $i=1,\ldots,N$, $d_n^{i}$ is distributed either as an asymmetric Bernoulli (see \eqref{eq:det-proj}) or Uniform $U[-\eta,\eta]$ for some $\eta >0$ (see Remark \ref{remark:unif}).
\begin{itemize}
\item \textbf{\emph {Function evaluation 1} }\\ \hspace{4em} Obtain $y_n^+ = f(\theta_n+\delta_n d_n) + \xi_n^+$.
\item \textbf{\emph {Function evaluation 2} }\\ \hspace{4em} Obtain $y_n^- = f(\theta_n-\delta_n d_n) + \xi_n^-$.
\item \textbf{\emph {Function evaluation 3} }\\ \hspace{4em} Obtain $y_n = f(\theta_n) + \xi_n$.
\item \textbf{\emph {Newton step}}\\ \hspace{4.2em} Update the parameter and Hessian as follows:
%\begin{align*}
%		x_{n+1} = & \; x_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(x_n), \\
%\overline H_n = &\; (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n),
%\end{align*}
\begin{align*} 
\theta_{n+1} = \,& \theta_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(\theta_n),\\
\overline H_n =\,& (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n).
\end{align*}
where $\widehat H_n$ and $\widehat \Psi_n$ are chosen according to \eqref{eq:2rdsa-estimate-ber} and \eqref{eq:psinhat}, respectively. 
\end{itemize}

@@

Algorithm \ref{alg:structure} presents the pseudocode and we describe the individual component of 2RDSA-IH below.
\section{Function evaluations}
Let $\delta_n, n\geq 0$ denote a sequence of diminishing positive real numbers and $d_n = (d_n^1,\ldots,d_n^N)\tr$ denote a random perturbation vector at instant $n$,
where the perturbations $\{d_n^i, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d. and distributed  as follows: 
\begin{equation}
\label{eq:det-proj}
 d_n^i =
  \begin{cases}
   -1 &  \text{ w.p. } \dfrac{(1+\epsilon)}{(2+\epsilon)}, \\
   1+\epsilon &  \text{ w.p. } \dfrac{1}{(2+\epsilon)},
  \end{cases}
\end{equation}
with $\epsilon>0$ being a constant that can be chosen to be arbitrarily small.

@@

\section{Improved Hessian estimation}
The Hessian estimate $\widehat H_n$ can be simplified as follows: 
\begin{align}
\widehat H_n & = M_n \left(\dfrac{y_n^+ + y_n^- - 2 y_n}{\delta_n^2}\right) \nonumber \\
& =  M_n \left[\left(\dfrac{f(\theta_n+\delta_n d_n) + f(\theta_n-\delta_n d_n) - 2 f(\theta_n)}{\delta_n^2}\right) \right. +\left. \left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2}\right)\right] \nonumber \\
& = M_n \left(d_n\tr \nabla^2 f(\theta_n) d_n +  O(\delta_n^2) + \left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2} \right)\right).\label{eq:h0}
%& = M_n \left(d_n\tr \nabla^2 f(x_n) d_n +  O(\delta_n^2) + O(\delta_n^{-2})\right). \label{eq:h0}
\end{align}
For the first term on the RHS above, note that 
\begin{align}
&\E[M_n \left(d_n\tr \nabla^2 f(\theta_n) d_n\right) \mid \F_n] =   \E\left[\left. M_n \times\right.\right.\left.\left.\left(\sum\limits_{i=1}^{N-1} (d_n^i)^2 \nabla^2_{ii} f(\theta_n) + 2\sum\limits_{i=1}^N\sum\limits_{j=i+1}^N d_n^i d_n^j \nabla^2_{ij} f(\theta_n) \right)\right| \F_n\right]. \label{eq:h1}
\end{align}
In analyzing the $l$th diagonal term of the above expression, the following zero-mean term appears (see the proof of Lemma 4 in \cite{prashanth2015rdsa}):
\begin{align}
& \E\left[\left. \left([M_n]_{D}\right)_{l,l} \left(2\sum\limits_{i=1}^{N-1}\sum\limits_{j=i+1}^N d_n^i d_n^j \nabla^2_{ij} f(\theta_n)\right)\right| \F_{n}\right] = 0,\label{eq:diagzero}
\end{align}
where for any matrix $M$, $[M]_{D}$ refers to a matrix that retains only the diagonal entries of $M$ and replaces all the remaining  entries with zero, and $\left([M]_{D}\right)_{i,j}$ refers to the $(i,j)$th entry in $[M]_D$. We shall also use $[M]_{N}$ to refer to a matrix that retains only the off-diagonal entries of $M$, while replaces all the diagonal entries with zero.

@@

In analyzing the off-diagonal term ($(k,l)$ where $k < l$) of \eqref{eq:h1}, the following zero-mean term appears:
\begin{align}
& \E\left[\left.\left([M_n]_{N}\right)_{k,l}   \left(\sum\limits_{i=1}^N (d_n^i)^2 \nabla^2_{ii} f(\theta_n)\right)\right| \F_n \right] = 0. 
\end{align}
The term on the LHS above, denoted by $\Psi_{n}^{2}(\nabla^2 f(\theta_n))$, can be written in matrix form as follows: 
\begin{align}\label{eq:ndmat}
\Psi_{n}^{2}(\nabla^2 f(\theta_n)) = [M_n]_{N}\left(d_{n}\tr \, [\nabla^2 f(\theta_n)]_{D} \, d_{n}\right).
\end{align}
From the foregoing, the per-iteration Hessian estimate $\widehat H_n$ can be re-written as follows:
\begin{align}
 \E\left[\left.\widehat H_n\right| \F_n\right] = & \nabla^2 f(\theta_n) + \E\left[\left.\Psi_{n}(\nabla^2 f(\theta_n))\right| \F_n\right]  +  O(\delta_n^2)+\E\left[\left.\left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2} \right)\right| \F_n\right], \label{eq:hnhat}
\end{align}
where, for any matrix $H$, 
\begin{align}
\Psi_{n}(H) &= \Psi_{n}^{1}(H) + \Psi_{n}^{2}(H)\nonumber\\
&= [M_n]_{D}\left(d_{n}\tr \, [H]_{N} \, d_{n}\right) +  [M_n]_{N}\left(d_{n}\tr \, [H]_{D} \, d_{n}\right).\label{eq:psi}
\end{align}
In the RHS of \eqref{eq:hnhat}, it is easy to see that  the second term involving $\Psi_{n}$ and the last term involving the noise are zero-mean. Moreover, since the noise is bounded by assumption, the last term in \eqref{eq:hnhat} vanishes asymptotically at the rate $O(\delta_n^{-2})$. So, the error in estimating the Hessian is due to the second term, which involves the perturbations $d_n$. This motivates the term $\widehat \Psi_n$ in the update rule \eqref{eq:e2rdsa}. 
 %and using the fact that $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n\right] = 0$

@@

\section{Convergence analysis}
\label{sec:2rdsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{enumerate}[label=(\textbf{C\arabic*})]
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1 i_2 i_3 i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For each $i=1,\ldots,N$ and any $\rho>0$, 
$P(\{ \bar f_{ni} (\theta_n) \ge 0 \text{ i.o}\} \cap \{ \bar f_{ni} (\theta_n) < 0 \text{ i.o}\} \mid \{ |\theta_{ni} - x^*_i| \ge \rho\quad \forall n\}) =0.$

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (x-x^*)_i \bar f_{ni}(x)}{\sum_{i \in S} (x-x^*)_i \bar f_{ni}(x)}               \right| < 1 \text{ a.s.}$$
for all $|(x-x^*)_i| < \tau$ when $i \notin S$ and $|(x-x^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_1$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{enumerate}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (C1)-(C8) are identical to that in \cite{prashanth2015rdsa}, while (C9) and (C10) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired by \cite{spall-jacobian}.

\begin{lemma}(\textbf{Bias in Hessian estimate})
\label{lemma:2rdsa-bias}
Under (C1)-(C10), with $\widehat H_n$ defined according to \eqref{eq:2rdsa-estimate-ber}, we have a.s. that\footnote{Here $\widehat H_n(i,j)$ and $\nabla^2_{ij}f(\cdot)$ denote the $(i,j)$th entry in the Hessian estimate $\widehat H_n$ and the true Hessian $\nabla^2 f(\cdot)$, respectively.}, for $i,j = 1,\ldots,N$,
\begin{align}
\left|\E\left[
\left. \widehat H_n(i,j) \right| \F_n \right] - \nabla^2_{ij} f(\theta_n)\right| = O(\delta_n^2).
\end{align} 
\end{lemma}
\begin{proof}
See Lemma 4 in \cite{prashanth2015rdsa}.
\end{proof}

\begin{theorem}(\textbf{Strong Convergence of Hessian})
\label{thm:2rdsa-H}
Under (C1)-(C10), we have that 
$$\theta_n \rightarrow \theta^*, \overline H_n \rightarrow \nabla^2 f(\theta^*) \text{ a.s. as } n\rightarrow \infty.$$ 
In the above, $\theta_n$ and $\overline H_n$ are updated according to \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}, respectively, $\widehat H_n$ defined according to \eqref{eq:2rdsa-estimate-ber} and the step-sizes $b_n$ are chosen as suggested in \eqref{eq:wieghts}. 
\end{theorem}
\begin{proof}
The first part of the claim regarding $\theta_n$ follows in exactly the same fashion as the proof of Theorem 5 in \cite{prashanth2015rdsa}.  
For proving the claim regarding $\overline H_n$, we closely follow the approach used to prove a corresponding result for 2SPSA (see Theorem 1 in \cite{spall-jacobian}). 
The first step is to prove the following:
\begin{align}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \widehat \Psi_k - \E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} \rightarrow 0.
\label{eq:step1}
\end{align}

By a completely parallel argument to that used in the proof of Theorem 1 in \cite{spall-jacobian}, we obtain: For any $i,j = 1,\ldots,N$,
\begin{align*}
\E \left[\left((\widehat {H}_k)_{i,j} - (\widehat {\Psi}_k)_{i,j} - \E((\widehat {H}_k)_{i,j} \mid \F_k)\right)^2\right] = O(\delta_k^{-4}).
\end{align*}
Now \eqref{eq:step1} follows by an application of Kronecker's Lemma along with the martingale convergence theorem (see Theorem 6.2.1 of \cite{lahaprobability}).

From Lemma \ref{lemma:2rdsa-bias}, we have 
$$ \E[ \widehat H_k \mid \F_k] = \nabla^2 f(\theta_n) + O(\delta_n^2) \text{ a.s.}$$
Since the Hessian is continuous near $\theta_n$ and $\theta_n$ converges almost surely to $\theta^*$, we have
% \footnote{Since assumptions (C1)-(C10) here are similar to that in \cite{prashanth2015rdsa}, Theorem 5 of \cite{prashanth2015rdsa} holds here as well. In particular, this implies almost sure convergence of $x_n$ to $x^*$.}
\begin{align*}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} 
=&\sum_{k=0}^n \dfrac{\delta_k^4 \left(\nabla^2 f(\theta_n) + O(\delta_n^2)\right)}{\sum_{i=0}^n \delta_i^4}\\
=&\sum_{k=0}^n \dfrac{\delta_k^4 \left(\nabla^2 f(x^*) + o(1)\right)}{\sum_{i=0}^n \delta_i^4}\\
&\rightarrow \nabla^2 f(x^*) \text{ a.s. as } n \rightarrow \infty.
\end{align*}
The last step above follows from Toeplitz Lemma (see p. 89 of \cite{lahaprobability}) after observing that $\sum_{i=0}^n \delta_i^4 \rightarrow \infty$ due to (C10). 
The main claim now follows since 
$$ \overline H_n = \sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \Psi_k \right)}{\sum_{i=0}^n \delta_i^4}.$$
\end{proof}

>>>>

\chapter{Second-order RDSA with improved hessian estimation (2RDSA-IH)}
\label{sec:2rdsa-ih}
The second-order RDSA with improved Hessian estimate performs an update iteration as follows:
\begin{align}
\label{eq:e2rdsa}
\theta_{n+1} = & \; \theta_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(\theta_n), \\
\overline H_n = & \; (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n),\label{eq:2rdsa-H}
\end{align}
where $\widehat\nabla f(\theta_n)$ is the estimate of $\nabla f(\theta_n)$, 
 %and this corresponds to  the uniform  and   asymmetric Bernoulli variant gradient estimates proposed in \cite{prashanth2015rdsa}.
$\overline H_n$ is an estimate of the true Hessian ${\nabla}^2 f(\cdot)$, $\Upsilon(\cdot)$ projects any matrix onto the set of positive definite matrices and $\{a_n, n\ge 0\}$ is a step-size sequence that satisfies standard stochastic approximation conditions. There are standard procedures such as Cholesky factorization, see \cite{bert22}, for projecting a given square matrix to the set of positive definite matrices. Moreover, in the vicinity of a local minimum, one expects the Hessian to be positive definite. In such a case, $\Upsilon$ will represent the identity operator.

@@

On the other hand, $\widehat H_n$ is identical to that in 2RDSA, i.e., it estimates the true Hessian in each iteration using three function evaluations. %Further, $\widehat H_0 = I$. 
For the sake of completeness, we first provide below the construction for $\widehat\nabla f(\theta_n)$ and $\widehat H_n$ using asymmetric Bernoulli perturbations, and subsequently we present the feedback term that reduces the error in $\widehat H_n$.

@@

 \item \textbf{Execution}: \\
 \For{$n \gets 0,1,2, \ldots, $} {
 \begin{itemize}
 \item Generate $\{d_n^{i}, i=1,\ldots,N\}$, independent of $\{d_m, m=0,1,\ldots,n-1\}$.  
 \item For any $i=1,\ldots,N$, $d_n^{i}$ is distributed according to either  asymmetric Bernoulli (see \eqref{eq:det-proj}) or Uniform $U[-\eta,\eta]$ distributions for some $\eta >0$ (see Remark \ref{remark:unif}).
\begin{itemize}
\item \textbf{\emph {Function evaluation 1} }\\ \hspace{4em} Obtain $y_n^+ = f(\theta_n+\delta_n d_n) + \xi_n^+$.
\item \textbf{\emph {Function evaluation 2} }\\ \hspace{4em} Obtain $y_n^- = f(\theta_n-\delta_n d_n) + \xi_n^-$.
\item \textbf{\emph {Function evaluation 3} }\\ \hspace{4em} Obtain $y_n = f(\theta_n) + \xi_n$.
\item \textbf{\emph {Newton step}}\\ \hspace{4.2em} Update the parameter and Hessian as follows:
%\begin{align*}
%		x_{n+1} = & \; x_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(x_n), \\
%\overline H_n = &\; (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n),
%\end{align*}
\begin{align*} 
\theta_{n+1} = \,& \theta_n - a_n \Upsilon(\overline H_n)^{-1}\widehat\nabla f(\theta_n),\\
\overline H_n =\,& (1-b_{n})  \overline H_{n-1} + b_{n} ( \widehat H_n - \widehat \Psi_n),
\end{align*}
where $\widehat H_n$ and $\widehat \Psi_n$ are chosen according to \eqref{eq:2rdsa-estimate-ber} and \eqref{eq:psinhat}, respectively. 
\end{itemize}

@@

Algorithm \ref{alg:structure} presents the pseudocode and we describe the individual components of 2RDSA-IH below.
\section{Function evaluations}
Let $\delta_n, n\geq 0$ denote a sequence of diminishing positive real numbers and $d_n = (d_n^1,\ldots,d_n^N)\tr$ denote a random perturbation vector at instant $n$,
where the perturbations $\{d_n^i, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d. and distributed  as follows: 
\begin{equation}
\label{eq:det-proj}
 d_n^i =
  \begin{cases}
   -1 &  \text{ w.p. } \dfrac{(1+\epsilon)}{(2+\epsilon)}, \\
   1+\epsilon &  \text{ w.p. } \dfrac{1}{(2+\epsilon)},
  \end{cases}
\end{equation}
with $\epsilon>0$ being a constant that can be chosen to be arbitrarily small.

@@

\section{Improved Hessian estimation}
The Hessian estimate $\widehat H_n$ can be simplified as follows: 
\begin{align}
\widehat H_n & = M_n \left(\dfrac{y_n^+ + y_n^- - 2 y_n}{\delta_n^2}\right) \nonumber \\
& =  M_n \left[\left(\dfrac{f(\theta_n+\delta_n d_n) + f(\theta_n-\delta_n d_n) - 2 f(\theta_n)}{\delta_n^2}\right) \right. +\left. \left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2}\right)\right] \nonumber \\
& = M_n \left(d_n\tr \nabla^2 f(\theta_n) d_n +  O(\delta_n^2) + \left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2} \right)\right).\label{eq:h0}
%& = M_n \left(d_n\tr \nabla^2 f(x_n) d_n +  O(\delta_n^2) + O(\delta_n^{-2})\right). \label{eq:h0}
\end{align}
For the first term on the RHS above, note that 
\begin{align}
&\E[M_n \left(d_n\tr \nabla^2 f(\theta_n) d_n\right) \mid \F_n] =   \E\left[\left. M_n \times\right.\right.\left.\left.\left(\sum\limits_{i=1}^{N-1} (d_n^i)^2 \nabla^2_{ii} f(\theta_n) + 2\sum\limits_{i=1}^N\sum\limits_{j=i+1}^N d_n^i d_n^j \nabla^2_{ij} f(\theta_n) \right)\right| \F_n\right]. \label{eq:h1-ch2}
\end{align}
In analyzing the $l$th diagonal term in the above expression, the following zero-mean term appears (see the proof of Lemma 4 in \cite{prashanth2015rdsa}):
\begin{align}
& \E\left[\left. \left([M_n]_{D}\right)_{l,l} \left(2\sum\limits_{i=1}^{N-1}\sum\limits_{j=i+1}^N d_n^i d_n^j \nabla^2_{ij} f(\theta_n)\right)\right| \F_{n}\right] = 0,\label{eq:diagzero}
\end{align}
where for any matrix $M$, $[M]_{D}$ refers to a matrix that retains only the diagonal entries of $M$ and replaces all the remaining  entries with zero, and $\left([M]_{D}\right)_{i,j}$ refers to the $(i,j)$th entry in $[M]_D$. We shall also use $[M]_{N}$ to refer to a matrix that retains only the off-diagonal entries of $M$, while replaces all the diagonal entries with zero.

@@

In analyzing the off-diagonal term ($(k,l)$ where $k < l$) of \eqref{eq:h1-ch2}, the following zero-mean term appears:
\begin{align}
& \E\left[\left.\left([M_n]_{N}\right)_{k,l}   \left(\sum\limits_{i=1}^N (d_n^i)^2 \nabla^2_{ii} f(\theta_n)\right)\right| \F_n \right] = 0. 
\end{align}
The term on the LHS above, denoted by $\Psi_{n}^{2}(\nabla^2 f(\theta_n))$, can be written in matrix form as follows: 
\begin{align}\label{eq:ndmat}
\Psi_{n}^{2}(\nabla^2 f(\theta_n)) = [M_n]_{N}\left(d_{n}\tr \, [\nabla^2 f(\theta_n)]_{D} \, d_{n}\right).
\end{align}
From the foregoing, the per-iteration Hessian estimate $\widehat H_n$ can be re-written as follows:
\begin{align}
 \E\left[\left.\widehat H_n\right| \F_n\right] = & \nabla^2 f(\theta_n) + \E\left[\left.\Psi_{n}(\nabla^2 f(\theta_n))\right| \F_n\right]  +  O(\delta_n^2)+\E\left[\left.\left(\dfrac{\xi_n^+ + \xi_n^- - 2 \xi_n}{\delta_n^2} \right)\right| \F_n\right], \label{eq:hnhat}
\end{align}
where, for any matrix $H$, 
\begin{align}
\Psi_{n}(H) &= \Psi_{n}^{1}(H) + \Psi_{n}^{2}(H)\nonumber\\
&= [M_n]_{D}\left(d_{n}\tr \, [H]_{N} \, d_{n}\right) +  [M_n]_{N}\left(d_{n}\tr \, [H]_{D} \, d_{n}\right).\label{eq:psi}
\end{align}
In the RHS of \eqref{eq:hnhat}, it is easy to see that  the second term involving $\Psi_{n}$ and the last term involving the noise are zero-mean. Moreover, since the noise is bounded by assumption, the last term in \eqref{eq:hnhat} vanishes asymptotically at the rate $O(\delta_n^{-2})$. So, the error in estimating the Hessian is due to the second term, which involves the perturbations $d_n$. This motivates the term $\widehat \Psi_n$ in the update rule \eqref{eq:e2rdsa}. 
 %and using the fact that $\E\left[\left.\xi_n^+ + \xi_n^- - 2\xi_n \right| \F_n\right] = 0$

@@

\section{Convergence analysis}
\label{sec:2rdsa-results}
We make the same assumptions as those used in the analysis of \cite{prashanth2015rdsa}, with a few minor alterations. The assumptions are listed below:
\begin{enumerate}[label=(\textbf{A\arabic*}),resume]
\item  The function
$f$ is four-times differentiable\footnote{Here $\nabla^4 f(\theta) = \dfrac{\partial^4 f (\theta)}{\partial \theta\tr \partial \theta\tr \partial \theta\tr \partial \theta\tr}$ denotes the fourth derivate of $f$ at $\theta$ and $\nabla^4_{i_1 i_2 i_3 i_4} f(\theta)$ denotes the $(i_1, i_2, i_3, i_4)$th entry of $\nabla^4 f(\theta)$, for $i_1, i_2, i_3,i_4=1,\ldots, N$.} with $\left|\nabla^4_{i_1 i_2 i_3 i_4} f(\theta) \right| < \infty$, for $i_1, i_2, i_3,i_4=1,\ldots, N$ and for all $\theta\in \R^N$.

@@

\item For each $i=1,\ldots,N$ and any $\rho>0$, 
$P(\{ \bar f_{ni} (\theta_n) \ge 0 \text{ i.o}\} \cap \{ \bar f_{ni} (\theta_n) < 0 \text{ i.o}\} \mid \{ |\theta_{ni} - \theta^*_i| \ge \rho\quad \forall n\}) =0.$

@@

\item For any $\tau >0$ and nonempty $S \subseteq \{1,\ldots,N\}$, there exists a $\rho'(\tau,S)>\tau$ such that 
$$ \limsup_{n\rightarrow \infty} \left| \dfrac{\sum_{i \notin S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}{\sum_{i \in S} (\theta-\theta^*)_i \bar f_{ni}(\theta)}               \right| < 1 \text{ a.s.}$$
for all $|(\theta-\theta^*)_i| < \tau$ when $i \notin S$ and $|(\theta-\theta^*)_i| \ge \rho'(\tau,S)$ when $i\in S$.
\item For some $\alpha_0, \alpha_1>0$ and for all $n$, $\E {\xi_n}^{2} \le \alpha_0$, $\E {\xi_n^{\pm}}^{2} \le \alpha_0$, $\E f(\theta_n)^{2} \le \alpha_1$,  $\E f(\theta_n\pm \delta_n d_n)^{2} \le \alpha_1$ and $\E \left(\left\| \Upsilon(\overline H_n) \right\|^2 \mid \F_n\right) \le \alpha_1$. 
\item  $\delta_n = \frac{\delta_0}{(n+1)^{\varsigma}}$, where $\delta_0 > 0$ and $0 < \varsigma \le 1/8$.
\end{enumerate}
The reader is referred to Section II-B of \cite{prashanth2015rdsa} for a detailed discussion of the above assumptions. We remark here that (C1)-(C8) are identical to assumptions in \cite{prashanth2015rdsa}, while (C9) and (C10) introduce minor additional requirements on $\left\| \Upsilon(\overline H_n \right\|^2$ and $\delta_n$, respectively and these are inspired from \cite{spall-jacobian}.

\begin{lemma}(\textbf{Bias in Hessian estimate})
\label{lemma:2rdsa-bias}
Under (C1)-(C10), with $\widehat H_n$ defined according to \eqref{eq:2rdsa-estimate-ber}, we have a.s. that\footnote{Here $\widehat H_n(i,j)$ and $\nabla^2_{ij}f(\cdot)$ denote the $(i,j)$th entries in the Hessian estimate $\widehat H_n$ and the true Hessian $\nabla^2 f(\cdot)$, respectively.}, for $i,j = 1,\ldots,N$,
\begin{align}
\left|\E\left[
\left. \widehat H_n(i,j) \right| \F_n \right] - \nabla^2_{ij} f(\theta_n)\right| = O(\delta_n^2).
\end{align} 
\end{lemma}
\begin{proof}
See Lemma 4 in \cite{prashanth2015rdsa}.
\end{proof}

\begin{theorem}(\textbf{Strong Convergence of Hessian})
\label{thm:2rdsa-H}
Under (C1)-(C10), we have that 
$$\theta_n \rightarrow \theta^*, \overline H_n \rightarrow \nabla^2 f(\theta^*) \text{ a.s. as } n\rightarrow \infty.$$ 
In the above, $\theta_n$ and $\overline H_n$ are updated according to \eqref{eq:e2rdsa} and \eqref{eq:2rdsa-H}, respectively, $\widehat H_n$ is defined according to \eqref{eq:2rdsa-estimate-ber} and the step-sizes $b_n$ are chosen as suggested in \eqref{eq:wieghts}. 
\end{theorem}
\begin{proof}
The first part of the claim regarding $\theta_n$ follows in exactly the same fashion as the proof of Theorem 5 in \cite{prashanth2015rdsa}.  
For proving the claim regarding $\overline H_n$, we closely follow the approach used to prove a corresponding result for 2SPSA (see Theorem 1 in \cite{spall-jacobian}). 
The first step is to prove the following:
\begin{align}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \widehat \Psi_k - \E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} \rightarrow 0.
\label{eq:step1}
\end{align}

By a completely similar argument to that used in the proof of Theorem 1 in \cite{spall-jacobian}, we obtain: For any $i,j = 1,\ldots,N$,
\begin{align*}
\E \left[\left((\widehat {H}_k)_{i,j} - (\widehat {\Psi}_k)_{i,j} - \E((\widehat {H}_k)_{i,j} \mid \F_k)\right)^2\right] = O(\delta_k^{-4}).
\end{align*}
Now \eqref{eq:step1} follows by an application of Kronecker's Lemma along with the martingale convergence theorem (see Theorem 6.2.1 of \cite{lahaprobability}).

From Lemma \ref{lemma:2rdsa-bias}, we have 
$$ \E[ \widehat H_k \mid \F_k] = \nabla^2 f(\theta_k) + O(\delta_k^2) \text{ a.s.}$$
Since the Hessian is continuous near $\theta_n$ and $\theta_n$ converges almost surely to $\theta^*$, we have
% \footnote{Since assumptions (C1)-(C10) here are similar to that in \cite{prashanth2015rdsa}, Theorem 5 of \cite{prashanth2015rdsa} holds here as well. In particular, this implies almost sure convergence of $x_n$ to $x^*$.}
\begin{align*}
\sum_{k=0}^n \dfrac{\delta_k^4 \left(\E(\widehat H_k \mid \F_k)\right)}{\sum_{i=0}^n \delta_i^4} 
=&\sum_{k=0}^n \dfrac{\delta_k^4 \left(\nabla^2 f(\theta_k) + O(\delta_k^2)\right)}{\sum_{i=0}^n \delta_i^4}\\
=&\sum_{k=0}^n \dfrac{\delta_k^4 \left(\nabla^2 f(\theta^*) + o(1)\right)}{\sum_{i=0}^n \delta_i^4}\\
&\rightarrow \nabla^2 f(\theta^*) \text{ a.s. as } n \rightarrow \infty.
\end{align*}
The last step above follows from Toeplitz Lemma (see p. 89 of \cite{lahaprobability}) after observing that $\sum_{i=0}^n \delta_i^4 \rightarrow \infty$ due to (C10). 
The main claim now follows since 
$$ \overline H_n = \sum_{k=0}^n \dfrac{\delta_k^4 \left(\widehat H_k - \Psi_k \right)}{\sum_{i=0}^n \delta_i^4}.$$
\end{proof}
